Model Checking

### 2023-05-23 owen/Write Ups/02_more_eda.qmd
writing some code to get the versions of the models James shared somewhat up and running, have it ready to fit them on the cluster also

---
title: "Model Checking"
author: Owen G. Ward
date: 04/17/2023
format: 
  html:
    toc: true
    toc-location: left
  # pdf
bibliography: refs.bib
---

@@

@@

mcmc_hist(fit5$draws(variables = c("delta", "mu3", "tau3", "gamma1", "gamma2")))
prob_positive(fit5$draws(), param = "delta")
```

@@

```{r get all bullet games}

all_bullet <- lichess_data %>% 
  filter(Event == "Rated Bullet game")

@@

@@

>>>>

---
title: "Model Checking"
author: Owen G. Ward
date: 04/17/2023
format: 
  # html:
  #   toc: true
  #   toc-location: left
  pdf
bibliography: refs.bib
---

@@

```{r prob positive fit3 beta}
#| echo: true
prob_positive(fit3_ave$draws())
```

@@

mcmc_hist(fit5$draws(variables = c("delta", "mu3", "tau3", "gamma1", "gamma2")))

```{r}
#| echo: true
prob_positive(fit5$draws(), param = "delta")
```

@@

```{r get all bullet games}
all_bullet <- lichess_data %>%
  filter(Event == "Rated Bullet game")

@@

#### First Model all Bullet

@@

#### Separating out History
